### 2024-08-23 Tables/fp_always_estimators_mort_tab.tex
add tables for appendix, various estimators

\caption{\label{tab:main_twfe_match}Effect of Clinically Trained Executive, Various Estimations}
\centering
\begin{tabular}[t]{lcccccl}
\toprule
\multicolumn{1}{c}{\underline{ }} & \multicolumn{3}{c}{\underline{Readmission Rate}} & \multicolumn{3}{c}{\underline{Mortality Rate}} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{TWFE} & \multicolumn{1}{c}{Matched} & \multicolumn{1}{c}{SC} & \multicolumn{1}{c}{TWFE} & \multicolumn{1}{c}{Matched} & \multicolumn{1}{c}{SC} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6} \cmidrule(l{3pt}r{3pt}){7-7}
 & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
Ever Clinical Exec x Post Program & 0.42$^{**}$ & 0.65$^{*}$ & 0.25 & 0.11 & 0.03 & 0.06\\
 & (0.15) & (0.3) & (0.14) & (0.15) & (0.4) & (0.12)\\
 &  &  &  &  &  & \\
Hospital FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
Year FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\addlinespace
Observations & 2,387 & 1,025 & 1,640 & 2,381 & 1,023 & 1,640\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:forprofit_mort_estimators}Compare For-Profit to Types of Leadership (Mortality Rates), Various Estimations}
\centering
\begin{tabular}[t]{lcccccl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Compare to Always Clinical Exec} & \multicolumn{3}{c}{Compare to Never Clinical Exec} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{TWFE} & \multicolumn{1}{c}{Matched} & \multicolumn{1}{c}{SC} & \multicolumn{1}{c}{TWFE} & \multicolumn{1}{c}{Matched} & \multicolumn{1}{c}{SC} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6} \cmidrule(l{3pt}r{3pt}){7-7}
 & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
For-Profit x Post Program & 0.03 & 0.09 & -0.16 & 0.06 & 0.05 & 0.03\\
 & (0.14) & (0.45) & (0.2) & (0.07) & (0.11) & (0.1)\\
 &  &  &  &  &  & \\
Hospital FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
Year FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\addlinespace
Observations & 2,660 & 660 & 2,660 & 3,820 & 1,790 & 3,820\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

### 2024-08-23 Tables/fp_always_estimators_read_tab.tex
add tables for appendix, various estimators

\caption{\label{tab:forprofit_mort_estimators}Compare For-Profit to Types of Leadership (Mortality Rates), Various Estimations}
\centering
\begin{tabular}[t]{lcccccl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Compare to Always Clinical Exec} & \multicolumn{3}{c}{Compare to Never Clinical Exec} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{TWFE} & \multicolumn{1}{c}{Matched} & \multicolumn{1}{c}{SC} & \multicolumn{1}{c}{TWFE} & \multicolumn{1}{c}{Matched} & \multicolumn{1}{c}{SC} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6} \cmidrule(l{3pt}r{3pt}){7-7}
 & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
For-Profit x Post Program & 0.03 & 0.09 & -0.16 & 0.06 & 0.05 & 0.03\\
 & (0.14) & (0.45) & (0.2) & (0.07) & (0.11) & (0.1)\\
 &  &  &  &  &  & \\
Hospital FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
Year FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\addlinespace
Observations & 2,660 & 660 & 2,660 & 3,820 & 1,790 & 3,820\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:forprofit_estimators}Compare For-Profit to Types of Leadership (Readmission Rates), Various Estimations}
\centering
\begin{tabular}[t]{lcccccl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Compare to Always Clinical Exec} & \multicolumn{3}{c}{Compare to Never Clinical Exec} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{TWFE} & \multicolumn{1}{c}{Matched} & \multicolumn{1}{c}{SC} & \multicolumn{1}{c}{TWFE} & \multicolumn{1}{c}{Matched} & \multicolumn{1}{c}{SC} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6} \cmidrule(l{3pt}r{3pt}){7-7}
 & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
For-Profit x Post Program & -0.37$^{*}$ & -0.28 & -0.43$^{*}$ & -0.03 & -0.08 & 0.09\\
 & (0.15) & (0.44) & (0.19) & (0.07) & (0.12) & (0.1)\\
 &  &  &  &  &  & \\
Hospital FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
Year FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\addlinespace
Observations & 2,660 & 660 & 2,660 & 3,820 & 1,790 & 3,820\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

### 2024-08-23 Tables/signal_manage_estimators_mort_tab.tex
add tables for appendix, various estimators

\caption{\label{tab:forprofit_estimators}Compare For-Profit to Types of Leadership (Readmission Rates), Various Estimations}
\centering
\begin{tabular}[t]{lcccccl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Compare to Always Clinical Exec} & \multicolumn{3}{c}{Compare to Never Clinical Exec} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{TWFE} & \multicolumn{1}{c}{Matched} & \multicolumn{1}{c}{SC} & \multicolumn{1}{c}{TWFE} & \multicolumn{1}{c}{Matched} & \multicolumn{1}{c}{SC} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6} \cmidrule(l{3pt}r{3pt}){7-7}
 & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
For-Profit x Post Program & -0.37$^{*}$ & -0.28 & -0.43$^{*}$ & -0.03 & -0.08 & 0.09\\
 & (0.15) & (0.44) & (0.19) & (0.07) & (0.12) & (0.1)\\
 &  &  &  &  &  & \\
Hospital FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
Year FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\addlinespace
Observations & 2,660 & 660 & 2,660 & 3,820 & 1,790 & 3,820\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:signal_manage_mort_estimators}Signaling vs. Managing Decomp. (mortmission Rates), Various Estimations}
\centering
\begin{tabular}[t]{lcccccl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Signaling Effect} & \multicolumn{3}{c}{Managing Effect} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{TWFE} & \multicolumn{1}{c}{Matched} & \multicolumn{1}{c}{SC} & \multicolumn{1}{c}{TWFE} & \multicolumn{1}{c}{Matched} & \multicolumn{1}{c}{SC} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6} \cmidrule(l{3pt}r{3pt}){7-7}
 & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
Estimate & -0.01 & -0.23 & 0.02 & 0.14 & -0.05 & 0.11\\
 & (0.08) & (0.18) & (0.06) & (0.11) & (0.28) & (0.08)\\
 &  &  &  &  &  & \\
Hospital FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
Year FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\addlinespace
Observations & 3,005 & 670 & 3,005 & 1,595 & 320 & 2,040\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}
